An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-07-08 Tex/elsevier/trindade_appliedenergy_rev1.tex
reviewed Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution. \textcolor{red}{We present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing. \textcolor{red}{We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool}.
\end{abstract}

@@

\textcolor{red}{In this study, our focus is not on a novel criteria or optimization objectives. Instead, our novelty relies on an effective approach on the pursuit of the optimal solution using formal methods, which outperforms existing state-of-the-art simulation tools.}

@@

Our work makes three major contributions. \textbf{First}, the use of automated 
symbolic verification methods in electrical systems was uncommon in recent 
prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
method together with user requirements and environment constraints, 
and our synthesis algorithm based on symbolic model checking 
can find the optimal solution in technical and economical terms. 
\textbf{Second}, we evaluate different state-of-art symbolic software 
verifiers with the goal of obtaining the best performance in our verification 
back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
on the pursuit of the optimal solution of PV system design using formal methods, which outperforms 
existing state-of-the-art simulation tools.}

>>>>

\begin{abstract}
There exist various methods and tools to size solar photovoltaic systems; however, these existing tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution. \textcolor{red}{Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis, with a particular focus on computer optimization methods instead of criteria or objectives, which were investigated in prior studies over the last two decades}. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound \textcolor{red}{cost} via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing. \textcolor{red}{We also present a comparative with a specialized simulation tool over real PV systems to show the effectiveness of our approach, which is able to provide more accurate results of optimal sizing of stand-alone PV systems than that existing simulation tool}.
\end{abstract}

@@

\textcolor{red}{Note that in this study, our focus is not on a novel criteria or even optimization objectives. Instead, our novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.}

@@

Our work makes three major contributions. \textbf{First}, the use of automated 
symbolic verification methods in electrical systems was uncommon in recent 
prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing 
optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, 
charge controllers, inverters, and batteries) can be fed to our proposed synthesis 
method together with user requirements and environment constraints, 
and our synthesis algorithm based on symbolic model checking 
can find the optimal solution in technical and economical terms. 
\textbf{Second}, we evaluate different state-of-art symbolic software 
verifiers with the goal of obtaining the best performance in our verification 
back-end for synthesizing optimal PV systems, \textcolor{red}{being the first work that performs this type of comparative.}
\textcolor{red}{\textbf{Third}, our experimental results show that our synthesis method is an effective and efficient approach 
on the pursuit of the optimal solution of PV systems using formal methods, which outperforms 
existing state-of-the-art simulation tools. As a result, our study marks the first application of a sound
and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems.
Thus, we considerably advance the state-of-the-art in applied energy over the last two decades 
with the goal of optimally designing PV systems.}
